What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-07 android-stacks.tex
merging introductions - step 1

\subsection{Georgios's Introduction}

Modern applications have to cope with an increasing number of abnormal
computation states that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware. The exception handling
mechanism~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions. When an exception is
caught by the program's exception handling code, the program has the opportunity
to assess the conditions that caused the fault and either recover the
computation or abort. An exception that is not caught by an exception handler
leads to a program crash. In most programming languages with exceptions, a crash
usually causes debugging information to emited by the language runtime to help
the programmer identify and fix the reason of the crash. The debugging
information is typical a stack trace, which includes an explanatory message and
the execution stack frame when the exception occurred. In Java, stack trace
consists of an ordered list of methods that were active on the call stack before
the exception occurred.

Although the exception handling mechanism has been the target of several studies
(e.g.~\cite{miller1997issues,Robil00,shah2010understanding,
garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}),
the exception handling code is often generally poorly understood and the least
tested part of software systems~\cite{coelho2011unveiling}. Similarily to source
code, current works focus their exception handling analysis on either static
(source code-based) or dynamic (runtime-based) analysis methods. Neither method
can explore the full execution space of a program and therefore they both fail
to account for exceptions caused by rutime issues (e.g. resource depletion) or
dynamically loaded code. Exception stack traces, when available, enable the
post-mortem analysis of exception handling behaviours of programs and
concequently the evaluation of exception handling mechanisms in programming
languages.

>>>>

\subsection{Georgios's and Roberta Merged Introduction}

Modern applications have to cope with an increasing number of abnormal
computation states that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware. The exception handling
mechanism~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions. When an exception is
caught inside the application by the program's exception handling code, 
the application has the opportunity
to assess the conditions that caused the fault and either recover from them or abort. 
An exception that remains uncaught (is not caught by an exception handler)
leads to a program crash. In most programming languages with embedded exception handling mechanism, when a crash happens usually the language runtime 
agenerates debugging information to help
the programmer identify and fix the reason of the crash. The debugging
information is typical a stack trace, which includes an explanatory message and
the execution stack frame when the exception occurred. In Java, stack trace
consists of an ordered list of methods that were active on the call stack before
the exception occurred.

Although the exception handling mechanism has been the target of several studies
(e.g.~\cite{miller1997issues,Robil00,shah2010understanding,
garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}),
the exception handling code is often generally poorly understood and the least
tested part of software systems~\cite{coelho2011unveiling}.

%Similarily to source
%code, 
%TODO GEORGIOUS I DID NOT UNDERESTA.ND THE IDEA OF THE PREVIOUS SENTENCE

Such studies  perform the analysis of exception handling code based  either on static
(source code-based) analysis or dynamic (runtime-based) testing methods. Neither of such methods, however,
can explore the full execution space of a program and therefore they both fail
to account for exceptions implicitly signaled by rutime environment (e.g. resource depletion) or
dynamically loaded code. Exception stack traces, when available, enable the
post-mortem analysis of exception handling behaviours of programs and
concequently the evaluation of exception handling mechanisms in programming
languages.
